Solar jet observed at the limb in SDO/SST

### 2016-05-14 paper/ms_temp_paper.tex
Some temperature map intro

Now the temperature profile

>>>>

One method for testing whether jets have any effect on the atmosphere, is to inspect the temperature and surrounding environment. 
The tool we use to inspect this is the method highlighted in \cite{Leonard2014}. 
The authors use a Differential Emission Measure (DEM) to obtain a temperature response from the SDO/AIA measurements.
The temperature response is a combination of the wavelength response from the instrument and the contribution function which describes the emission from a given temperature.
When using such a scheme, we need to decide on a general DEM profile to be applied to all pixels.
Utilising a narrow Gaussian seems to provide the most accurate values when compared to synthetic observations.
